Regime transition identification for basin's governance challenges of water use

### 2020-11-17 tex/main/manuscript.tex
changed into governance context  on the whole

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A schematic diagram for understanding the changing relationship between social development and water utilization.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three dimensions (stress, priority and configuration) of water resources utilization. Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis. (1) Stress of water utilization shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not. (2) Priority of water utilization can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies. (3) configuration can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed. We presume that water utilization regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the changes after combining the three dimensions. Because the above three dimensions are changing with the development of society, their combined water resource utilization status is also different. When abrupt transitions occur during this process, they may indicate a regime shift in water utilization, so we need an indicator to monitor this change.
	}
	\label{fig:framework}
\end{figure*}

\section*{Results}
\subsection*{Water utilization regimes}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWGI index. 
	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWGI have three periods in changing trend.
	\textbf{B,} Changing slopes of each period.
	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Stress, priority and configuration are the main positive contributor of P1, P2 and P3, respectively.
	}
	\label{fig:IWGI}
\end{figure}

% 这一节主要展示IWGI的变化趋势和WUR的划分
With two significant points, the changing trend of IWGI index are detected into three periods (Figure~\ref{fig:IWGI}A). 
Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWGI}B and Figure~\ref{fig:IWGI}C).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while priority and configuration of the water utilization had slight negative contribution (-11\% and -20\%).
% 第二阶段
In the second period (P2, 1979-1994), though contributions of priority and configuration turned into positive, the IWGI index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1). 
% 第三阶段
However, as the further increasing of positive contributions of priority (75\%) and configuration (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C). When the points are bellow this line, the contribution ratio of configuration is lower than that of priority, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}

% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
Taken together, each period has the unique most striking positive contributor to IWGI, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses. After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

% %tag 结果2
% \subsection*{Differences between water utilization regimes}
% % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
% The differences between the water utilization regimes are reflected in changes of all three dimensions.

% % 从阶段一到阶段二，水资源压力的变化最为明显
% Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).   
% % 1. 水资源丰富，耗水量少且灵活用水
% In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig. S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig. S5). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

% % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts. 
% % 首先是用水比例的变化
% Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
% % 再讨论用水格局的变化
% However, configuration of water utilization, whose contributions to the IWGI are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).

% tag 结果3
\subsection*{Causes of water utilization regime shifts}

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Drivers of water utilization regime shifts: economy growths, efficiency changes, and management practices.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

% 经济总量提升导致资源耗竭的加速。
Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S7). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
Secondly, efficiency of water utilization changed from the P2 to the P3.
While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes}A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B). 
However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig. S8). As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).

% 不断变化的管理模式。
Finally, changing water management practice contributed throughout all three periods. 
According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
In the P1, most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). 
Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).

@@

\subsection*{Water governance challenges along transition regimes}
% 我们发明的指数能同时关注水资源治理的三个关键方面。
The IWGI index we developed captures three key dimensions of water governance simultaneously: (water use stress, provision of water use and allocation for water use). 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Based on that, our results show that three distinct but sequential governance regimes within YRB, whose shifts have been caused by different environmental, economic, social or political aspects.
% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.

@@

% % 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
% At the beginning of P1, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S9). 
% % 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
% Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development.
% % 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
% At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure \cite{yellowriverarchivesOrganizationalHistoryYellow2004}, and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% % 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
% As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.

% % 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% % 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
% The regime nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. As the most obvious performance, the Yellow River was dried up for several times since 1972 (\textit{SI Appendix} Fig. S10). 
% % 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
% During the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% % 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
% Since then, the expansion trend of agriculture has been constrained (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the Reform and Opening-up policy. In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

% % 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
% The next regime shift was not occurred until a significant increase in water use efficiency since about 1993. 
% % 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
% After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig. S9).
% % 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
% A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture. As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig. S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).

% In short, agricultural expansion, industries and services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system. They have driven the YRB to change regimes twice between 1965 and 2013, which can be interpreted as a transition process along with social development.

\subsection*{Implications and future directions}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition framework of water utilization.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

% 上述过渡过程与稳态转换的关联可能是普遍的
The links between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic processes are gradually dominating human-water systems in most river basins.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage.
% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
In the framework, provisioning water utilization (agriculture, domestic or livestock) are dominated at the primal phase and social processes take over dominating with growths of industry and services in the followed phases, with coordinated considerations of water utilization over the whole basin (Figure~\ref{fig:summary}).

Three dimensions of water utilization are various throughout the transition. 
% 水资源压力
Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can respond to resource scarcity by better management or efficiency. Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig. S3). However, water utilization stresses changes a lot rather than always increasing, because constructions of reservoir and the increased water use efficiency were all played roles (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but converted to an energy industry zone now \cite{WillEnergyBases}. 
As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
% 水资源格局
Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed configuration.
% \cite{wangThirtyYearsYellow2018}. 
% However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories 
%\cite{wangThirtyYearsYellow2018}. 
% The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.

% 综上所述
By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary}B and Figure~\ref{fig:summary}C), with socio-economic processes dominated step by step. In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework. 
For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. 
In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.

>>>>

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A schematic diagram for understanding the changing relationship between social development and water governance.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three dimensions (stress, provision and allocation) of water resources governance. Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources governance changes along that axis. (1) Stress of water governance shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not. (2) provision of water governance can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies. (3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed. We presume that water governance regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the changes after combining the three dimensions. Because the above three dimensions are changing with the development of society, their combined water resource governance status is also different. When abrupt transitions occur during this process, they may indicate a regime shift in water governance, so we need an indicator to monitor this change.
	}
	\label{fig:framework}
\end{figure*}

\section*{Results}
\subsection*{Water governance regimes}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWGI index. 
	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWGI have three periods in changing trend.
	\textbf{B,} Changing slopes of each period.
	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Stress, provision and allocation are the main positive contributor of P1, P2 and P3, respectively.
	}
	\label{fig:IWGI}
\end{figure}

% 这一节主要展示IWGI的变化趋势和WUR的划分
With two significant points, the changing trend of IWGI index are detected into three periods (Figure~\ref{fig:IWGI}A). 
Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWGI}B and Figure~\ref{fig:IWGI}C).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while provision and allocation of the water governance had slight negative contribution (-11\% and -20\%).
% 第二阶段
In the second period (P2, 1979-1994), though contributions of provision and allocation turned into positive, the IWGI index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1). 
% 第三阶段
However, as the further increasing of positive contributions of provision (75\%) and allocation (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: provision; C: allocation). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between provision (P) and allocation (C). When the points are bellow this line, the contribution ratio of allocation is lower than that of provision, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}

% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
Taken together, each period has the unique most striking positive contributor to IWGI, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water governance regime dominated by lower stresses. After then, it experienced a shift to high stresses since 1978, with a change in the proportion of contributions between provision and allocation, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for provision, allocation and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

% %tag 结果2
% \subsection*{Differences between water governance regimes}
% % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
% The differences between the water governance regimes are reflected in changes of all three dimensions.

% % 从阶段一到阶段二，水资源压力的变化最为明显
% Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water governance stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).   
% % 1. 水资源丰富，耗水量少且灵活用水
% In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig. S3) and most of which were flexible water governance (\textit{SI Appendix} Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig. S5). As a result, water governance stress decreases during P1, but begins to rise rapidly in P2.

% % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, provision (Figure~\ref{fig:dimensions}B) and allocation (Figure~\ref{fig:dimensions}C) of water governance were keeping to enlarge their impacts. 
% % 首先是用水比例的变化
% Representing provision of water governance, increasing non-provisioning share of water governance were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
% % 再讨论用水格局的变化
% However, allocation of water governance, whose contributions to the IWGI are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).

% tag 结果3
\subsection*{Causes of water governance regime shifts}

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Drivers of water governance regime shifts: economy growths, efficiency changes, and management practices.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

% 经济总量提升导致资源耗竭的加速。
Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the provision of water use between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant governance way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S7). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
Secondly, efficiency of water use changed from the P2 to the P3.
While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes}A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B). 
However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
It means, water governance ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig. S8). As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).

% 不断变化的管理模式。
Finally, water policies and management practices contributed throughout all three periods. 
According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
In the P1, most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). 
Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).

@@

\subsection*{Water governance challenges along transition regimes}

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition framework of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

% 我们发明的指数能同时关注水资源治理的三个关键方面。
The IWGI index we developed captures three key dimensions of water governance simultaneously: (water use stress, provision of water use and allocation for water use). 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Based on that, our results show that three distinct but sequential governance regimes within YRB, whose shifts have been caused by different environmental, economic, social or political aspects.
% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.

@@

\subsection*{Implications and future directions}
\label{Outlook}

% 我们发展的指数捕捉了水治理的过渡制度，以一种相对全面但简单的方式
The index we developed (IWGI), captures the transition regimes of water governance with different challenges, in a relatively simple but comprehensive way.
% 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
It is important for scientists and decision makers to recognize the changing challenges for water governance, because development is not a panacea for all basin issues regarding sustainability.
% 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
For today's world, increasing water stresses on water use remains one of the greatest water governance challenges, while economic development provision strategies are still the main guideline to meet them. 
% 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
Although most large river basins improved water management and efficiency along with development, most studies still pessimistically point out that freshwater use is reaching planetary boundaries where human-water systems may collapse.
% 总的来说，这可能有两点主要原因。
Overall, there are probably two main reasons.
% 首先，效率悖论
Firstly, significant improvement in agricultural irrigation efficiency is usually accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency 
\cite{graftonParadoxIrrigationEfficiency2018}. 
% 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
Secondly, complicated structure of water allocation or provision under a governance regime dominated by hydro-social water cycle may lead the water governance more inflexible and damage to resilience of the basin
\cite{qinFlexibilityIntensityGlobal2019}.
% 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
At this point, we need corresponding comprehensive strategies to address the governance challenges, because the heart factors of are beyond the control of any related actor. 
% 基于对治理稳态的认识，我们可以为应对挑战创造有利条件，让利益相关者实现对社会和环境状况的预期，从而维持流域社会-生态系统的弹性。
Based on the understanding of governance regime transition, we can create favourable conditions for meeting the challenges and enabling stakeholders to realize their expectations of social and environmental changes, thus maintaining the resilience of the basin's socio-ecosystem.
% 总的来说，这些都有助于指导流域迈向可持续性。
Taken together, these have helped guide the basin towards sustainability.

%tag 研究方法
\matmethods{
Here, we constructed the Integrated Water Resources governance (IWGI) Index which consists of three dimensions and identified the changes periods of the index over time by change points detection. 
Each dimension is reflected by an independent indicator after normalization, and water governance regime were characterized by combination of impacts of each dimension in periods.
In addition, the contribution to changes of IWGI index along with each main indicators were decomposed and calculated separately for each regime (i.e. period).

	\subsection*{Integrated Water Resources governance (IWGI) Index}
	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
	Water resources governance system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):

	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
	\begin{itemize}
		\item Social development is usually accompanied by a change of provision in water use towards social and economic systems because of higher returns:
		$$ Dev. \propto P $$
		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
		\item Social development usually lead to more complex structure in allocation of water resources, which is a result of division and cooperation between regions and sectors for developing:
		$$ Dev \propto A $$ 
		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
		\item Further social development can only be achieved by effectively alleviating the water resource stresses generated in the process of development through technological means:
		$$ Dev \propto S^{-1} $$
	\end{itemize}
